\section{Theoretical predictions}
\label{sec:theory}

% \arc{Section 5: It's not too clear which model is used in which context, etc. At the moment this section is a bit confusing.}

% \arc{section 5 should spell out what's done for the branching fractions and non-ggH production modes.}

Differential cross sections may be used constrain physical parameters.
% 
In the case of Higgs boson production through gluon fusion, finite quark mass effects and moderate variations to Higgs couplings may manifest in distortions of the $\pth$ spectrum.
% 
We interpret the $\pth$ spectrum for gluon fusion in terms of modifications of the couplings of the Higgs boson using two models: one tailored to heavy quarks and thus sensitive to effects at high $\pt$~\cite{Grazzini:2017szg}, and the other considering the effect of lighter quarks in the gluon fusion loop~\cite{Bishara:2016jga}.
% 
Higgs boson production in association with bottom and top quarks is taken to scale quadratically with $\kappa_b$ and $\kappa_t$ respectively.
% 
The other production processes are taken to be independent of these couplings.
% 
The coupling modifiers are described within the context of the kappa-framework~\cite{LHCHiggsCrossSectionWorkingGroup:2012nn,Khachatryan:2016vau}:
% 
\begin{equation}
    \kappa_i^2
        = \frac{y_i}{y_i^\text{SM}}
        % = \frac{\sigma_i}{\sigma_i^\text{SM}}
    \,,
\end{equation}
% 
% where $\sigma_i$ is the production cross section of a Higgs boson resulting from the direct coupling to particle $i$.
% 
where $y_i$ is the Higgs boson coupling to particle $i$.
% 
The SM value of any $\kappa_i$ is equal to 1.


Recent developments in transverse momentum resummation procedures have allowed more accurate calculations of the $\pth$ spectrum when including the effects of lighter quarks on Higgs production through gluon fusion~\cite{Banfi:2013eda,Bozzi:2003jy,Becher:2010tm,Monni:2016ktx}.
% 
The $\pth$ spectrum for gluon fusion has been calculated for simultaneous variations of $\kappa_c$ and $\kappa_b$~\cite{Bishara:2016jga}, providing a novel approach to constrain these couplings via the $\pth$ spectrum.
% 
The variations are computed in Ref.~\cite{Bishara:2016jga} and we parameterize these with a quadratic polynomial for each bin of the differential production cross section, including an inhomogeneity due to the interference of the top quark with the bottom and charm quarks.
% 
The Higgs coupling to the top quark is fixed to its SM value in this model.
% 
% We parametrize these variations, taken precomputed as input from Ref.~\cite{Bishara:2016jga}, using a quadratic polynomial for each bin of the differential production cross section, including an inhomogeneity due to the interference of the top quark, whose coupling is fixed to its SM value in this model.
% 
% \arc{you mention coupling to top quark fixed to its SM value, and then introduce kt. This is contradictory, please specify in which case.}


A second model producing simultaneous variations of $\kappa_t$, $\cg$ and $\kappa_b$ by adding dimension-6 operators to the SM Lagrangian was built in Ref.~\cite{Grazzini:2017szg}.
% 
This study employs an analytic resummation performed up to next-to-next-to-leading logarithmic (NNLL) order for the lower $\pth$ region in order to obtain the $\pth$ spectrum at NNLO+NNLL accuracy.
% 
The dimension-6 operator whose coefficient is $\cg$ yields a direct coupling of the Higgs boson to the gluon, whose tensor structure corresponds to the heavy top mass limit.
% 
The derivation of $\cg$ is given in Ref.~\cite{Grazzini:2017szg} and the inclusive cross section is given by $\sigma \simeq \left| 12\cg + \kappa_t \right|^2 \sigma^\text{SM}$.
% 
% $\cg$ is defined according to the derivations described in Ref.~\cite{Grazzini:2017szg}, which yields a dependence of the inclusive cross section $\sigma \simeq \left| 12\cg + \kappa_t \right|^2 \sigma^\text{SM}$.
% 
Two other operators are included to describe modifications of $\kappa_t$ and $\kappa_b$.
% 
While the model allows simultaneous variation of all three coupling modifiers, we consider only simultaneous variations of $\kappa_t$ and $\cg$, and of $\kappa_t$ and $\kappa_b$.
% 
The precomputed spectra are taken as input from Ref.~\cite{Grazzini:2017szg} and are parametrized using a quadratic polynomial, neglecting the interference of the bottom and top quark in the gluon fusion loop.
% 
% In the case of differential cross sections, each cross section per bin has one parametrization.


% In order to map the finely binned theoretical predictions to the experimental binning, the theoretical spectrum is integrated within experimental bin boundaries.


The coupling modifiers affect not only the production cross section of the Higgs boson, but its branching fractions as well.
% 
Throughout our results we will consider the branching fractions to be scaling with the Higgs coupling modifiers.

